Manuscript

### 2015-02-02 inst/simulation/manuscript.Rmd
...

```{r figure-2}
study <- getStudy(scenario="A")
limits <- extent(study$studyArea$boundary)
iterations <- as.integer(c(1,6,3,2,5,31))
densities <- getEstimatedDensity(scenarios=scenarios[6], modelName=modelNames[1], iterations=iterations[6], year=year, sd=F, log=F)
year <- 2010
yearLayer <- paste0("X", year)
surveyRoutes <- getSurveyRouteLocations(scenarios=scenarios, modelName=modelNames[1], iterations=iterations, years=year)
#surveyRoutes <- rbind(surveyRoutes[surveyRoutes$intersections == FALSE,], surveyRoutes[surveyRoutes$intersections == TRUE,])
agents <- getAgentLocations(scenarios=scenarios, modelName=modelNames[1], iterations=iterations, years=year)
densities <- getEstimatedDensity(scenarios=scenarios, modelName=modelNames[1], iterations=iterations, year=year, sd=F, log=F)
# TODO: do not use scaling??
#densitiesScaled <- ddply(densities, .(scenario), function(x, yearLayer) { x[,yearLayer] <- scale(x[,yearLayer]); return(x) }, yearLayer=yearLayer)

@@

```{r table-1abc}
getPopulationSizesTable <- function(populationSizes, meanPopulationSizes, overEstimate, full=F, file) {
  library(plyr)
  x <- ddply(populationSizes, .(Scenario, modelName), function(x, overEstimate) {
    failed <- round((sum(x$Estimated >= overEstimate) / nrow(x)) * 100)
    if (any(abs(x$Estimated) == Inf)) return(data.frame(Intercept=NA, Slope=NA, R2=NA, Failed=failed))
    y <- lm(Estimated~Observed, x)
    return(data.frame(Intercept=round(coef(y)[1], 0), Slope=round(coef(y)[2], 2), R2=round(summary(y)$r.squared, 2), Failed=failed))
  }, overEstimate=overEstimate)

  y <- unique(meanPopulationSizes)
  y$Scenario <- y$scenario
  y$EstDev <- y$Estimated / y$True
  z <- plyr::join(x, y)
  z$Model <- prettyModelName(z$modelName)
  z$Scenario <- substr(z$Scenario, 1, 1)
  if (full) return(z)

  z <- z[,c("Scenario","Model","Slope","R2","EstDev","Failed")]
  z$EstDev <- round(z$EstDev, 2)
  if (!missing(file)) write.csv(z, file=file)
  return(z)
}

dir <- normalizePath(context$figuresDirectory)
getPopulationSizesTable(logPopulationSizes, logMeanPopulationSizes, overEstimate=log10(2000+1), file=file.path(dir, "table-1a.csv"))
getPopulationSizesTable(logPopulationSizes2000, logMeanPopulationSizes2000, overEstimate=log10(20000+1), file=file.path(dir, "table-1b.csv"))
getPopulationSizesTable(logPopulationSizes10Days, logMeanPopulationSizes10Days, overEstimate=log10(2000+1), file=file.path(dir, "table-1c.csv"))
```

>>>>

```{r figure-2}
study <- getStudy(scenario="A")
limits <- extent(study$studyArea$boundary)
iterations <- as.integer(c(1,6,3,2,5,31))
year <- 2010
yearLayer <- paste0("X", year)
surveyRoutes <- getSurveyRouteLocations(scenarios=scenarios, modelName=modelNames[1], iterations=iterations, years=year)
#surveyRoutes <- rbind(surveyRoutes[surveyRoutes$intersections == FALSE,], surveyRoutes[surveyRoutes$intersections == TRUE,])
agents <- getAgentLocations(scenarios=scenarios, modelName=modelNames[1], iterations=iterations, years=year)
densities <- getEstimatedDensity(scenarios=scenarios, modelName=modelNames[1], iterations=iterations, year=year, sd=F, log=F)
# TODO: do not use scaling??
#densitiesScaled <- ddply(densities, .(scenario), function(x, yearLayer) { x[,yearLayer] <- scale(x[,yearLayer]); return(x) }, yearLayer=yearLayer)

@@

```{r table-1abc}
getPopulationSizesTable <- function(populationSizes, meanPopulationSizes, overEstimate, full=F, file, ...) {
  library(plyr)
  x <- ddply(populationSizes, .(Scenario, modelName), function(x, overEstimate) {
    failed <- round((sum(x$Estimated >= overEstimate) / nrow(x)) * 100)
    if (any(abs(x$Estimated) == Inf)) return(data.frame(Intercept=NA, Slope=NA, R2=NA, Failed=failed, MeanProp=NA, SDProp=NA))
    y <- lm(Estimated~Observed, x)
    prop.mean <- mean(x$Estimated/x$Observed)
    prop.sd <- sd(x$Estimated/x$Observed)
    return(data.frame(Intercept=round(coef(y)[1], 0), Slope=round(coef(y)[2], 2), R2=round(summary(y)$r.squared, 2), Failed=failed, MeanProp=prop.mean, SDProp=prop.sd))
  }, overEstimate=overEstimate)

  y <- unique(meanPopulationSizes)
  y$Scenario <- y$scenario
  #y$EstDev <- y$Estimated / y$True
  z <- plyr::join(x, y)
  z$Model <- prettyModelName(z$modelName)
  z$Scenario <- substr(z$Scenario, 1, 1)
  if (full) return(z)

  z <- z[,c("Scenario","Model","Slope","R2","Failed","MeanProp","SDProp")]
  #z$EstDev <- round(z$EstDev, 2)
  z$MeanProp <- round(z$MeanProp, 2)
  z$SDProp <- round(z$SDProp, 2)
  if (!missing(file)) write.csv(z, file=file)
  return(z)
}

dir <- normalizePath(context$figuresDirectory)
table1 <- getPopulationSizesTable(populationSizes, meanPopulationSizes, overEstimate=2000)
logTable1 <- getPopulationSizesTable(logPopulationSizes, logMeanPopulationSizes, overEstimate=log10(2000+1), file=file.path(dir, "table-1a.csv"))
logTable1$MeanProp <- table1$MeanProp; logTable1$SDProp <- table1$SDProp; 
write.csv(logTable1, file=file.path(dir, "table-1a.csv"))

table2 <- getPopulationSizesTable(populationSizes2000, meanPopulationSizes2000, overEstimate=20000)
logTable2 <- getPopulationSizesTable(logPopulationSizes2000, logMeanPopulationSizes2000, overEstimate=log10(20000+1), file=file.path(dir, "table-1b.csv"))
logTable2$MeanProp <- table2$MeanProp; logTable2$SDProp <- table2$SDProp; 
write.csv(logTable2, file=file.path(dir, "table-2a.csv"))

table3 <- getPopulationSizesTable(populationSizes10Days, meanPopulationSizes10Days, overEstimate=2000)
logTable3 <- getPopulationSizesTable(logPopulationSizes10Days, logMeanPopulationSizes10Days, overEstimate=log10(2000+1), file=file.path(dir, "table-1c.csv"))
logTable3$MeanProp <- table3$MeanProp; logTable3$SDProp <- table3$SDProp; 
write.csv(logTable3, file=file.path(dir, "table-3a.csv"))
```
